---
title: "Interest Trend"
author: "Taketo Muroya"
output: 
  html_document:
    code_folding: hide
    highlight: textmate
---

```{r Setup, include=FALSE, results='hide', warning=FALSE}
library(knitr)
opts_chunk$set(fig.path="figures/", cache.path="cache/", 
               cache=FALSE,echo=TRUE,message=FALSE,warning=FALSE)
# Setting up
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(dplyr)
library(plotly)
#if (!require("devtools")) install.packages("devtools")
#devtools::install_github("PMassicotte/gtrendsR", force=TRUE)
library(gtrendsR)
```

How has people's interests in vegetarian changed over time? The data from "Google Trend" provides the monthly number of search volume in the U.S. from January 2004 to the present. It also offeres the number of search volume by state level.

```{r eval=F}
# get Vegetarian search
veg <- gtrends(keyword=c("vegetarian"), geo="US", time="all")
trend <- veg$interest_over_time
write.csv(trend, "data//trend.csv")
```

```{r, fig.width=10, fig.height=5}
trend <- read.csv("data//trend.csv", stringsAsFactors = FALSE)

# create trend by the loess smoothing 
trend$t <- c(1:nrow(trend))
smooth <- loess(trend$hits~trend$t, span=0.7)

# visualize Google search
plot_ly(trend, x=~date, y=~hits, type="scatter", mode="lines", name="Actual Search") %>%
  add_lines(x=~date, y=predict(smooth), name="Trend") %>%
  layout(title="Google Search 'Vegetarian'", legend = list(orientation="h"),
         xaxis=list(title="Time"), yaxis=list(title="Search Volume (Max=100)"),
         font=list(color="black"))
```

(This graph is interactive. You can examine dates and values by putting your cursor on it.) The Google search volume for "vegetarian" seems to be increasing recent years. In addition, people more often search "vegetarian" in November and January. This might be because vegetarians wonder what dish they should have on Thanksgiving or New Year.

```{r trend, fig.width=10, fig.height=5}
# search by state
# region_top <- veg$interest_by_region[1:8,]
# write.csv(region_top, "region_top.csv")
region_top <- read.csv("data//region_top.csv", stringsAsFactors = FALSE)

p1<-ggplot(region_top, aes(x=reorder(location, hits), y=hits))+
  geom_bar(fill='#4E79A7', stat="identity", position="identity", alpha=0.5)+
  xlab('')+ylab('Search Volume (Max=100)')+
  scale_y_continuous(breaks=seq(0,100,length=5))+coord_cartesian(ylim=c(0,100))+
  ggtitle("Top 8 States Searching 'Vegetarian'")+theme_hc()

# region_bottom <- veg$interest_by_region[44:51,]
# write.csv(region_bottom, "region_bottom.csv")
region_bottom <- read.csv("data//region_bottom.csv", stringsAsFactors = FALSE)

p2<-ggplot(region_bottom, aes(x=reorder(location, desc(hits)), y=hits))+
  geom_bar(fill="#E15759", stat="identity", position="identity", alpha=0.5)+
  xlab('State')+ylab('Search Volume (Max=100)')+
  scale_y_continuous(breaks=seq(0,100,length=5))+coord_cartesian(ylim=c(0,50))+
  ggtitle("Bottom 8 States Searching 'Vegetarian'")+theme_hc()

gridExtra::grid.arrange(p1, p2, ncol=1)
```

Most of the top 8 states are located in either east or west coast, while bottom 8 states are relatively located in a middle land. According to the 2016 US presidential election, top 8 states are all "Blue" state (Democratic) and bottom 8 states are all "Red" state (Republican). This mgiht indicate that liberal people are more interested in "vegetarian" than conservative people.

